Changes in Patterns of Geometric Sign Groupings as a Model of Social Dynamics Across Aurignacian Phases

### 2025-03-14 endofquarterpaper.qmd
update table caption

```{r}
#| label: tbl-aur-table
#| tbl-cap: "Table of data on Aurignacian periods [@Banks_dErrico_Zilhao_2013;  @Shao_Limberg_Klein_Wegener_Schmidt_Weniger_Hense_Rostami_2021; @Chu_Richter_2020; @Fletcher_Sánchez]"
#| tbl-cap-location: bottom

>>>>

```{r}
#| label: tbl-aur-table
#| tbl-cap: "Summary of chronological, cultural and environmental characteristics of Aurignacian periods [@Banks_dErrico_Zilhao_2013;  @Shao_Limberg_Klein_Wegener_Schmidt_Weniger_Hense_Rostami_2021; @Chu_Richter_2020; @Fletcher_Sánchez]"
#| tbl-cap-location: bottom
